Operation Mode Study in Cloud Manufacturing Ecosystem

### 2016-11-02 intro.tex
add background, need the environmental

% !TEX root = Eco-Model.tex
\section{Introduction}
The relationship among entities in a cloud manufacturing system become more complicated than that in existing manufacturing systems, since the integration of advanced technologies makes it possible for individual to make decisions depend on enriched information. Demanders prefer high quality of performance, while providers prefer high use rate of resource. A cloud platform operator prefers a fewer amount of registered resource when dealing with almost arriving needs for an easier maintenance. These preferences stimulate the emergence of good service pattern that will lead to the emergence operation mode in the cloud manufacturing ecosystem. Hence, it's important to identify a suitable operation mode to meet most of individuals' preference.

In this paper, an original operation mode is designed to describe the basic decision-makings in cloud manufacturing ecosystem, then three extensions, namely metabolism mode, incubation mode and outsourcing mode are proposed. Finally, an experiment to validate these synthetic operation modes are designed using an agent-based simulation method.

>>>>

% !TEX root = Eco-Model.tex
\section{Introduction}
Manufacturing activities consume kinds of resources (e.g. material, equipment, manpower, nature resource), which will resulting in substantial environmental issues. Properly arrange these resources to collaborate a manufacturing process is one of feasible approaches to reduce the waste during the consumption of resources, the concept of cloud manufacturing \cite{li2010cloud,Xu2012} provides a operating framework to realize the arrangement.

However, the relationship among entities in a cloud manufacturing system become more complicated than that in existing manufacturing systems, since the integration of advanced technologies makes it possible for individual to make decisions depend on enriched information.
In particular, \autoref{fig:originmode} shows the basic procedures that need three main entities to make decisions on. \textbf{Demander} is the entity that publish manufacturing task, it prefers high quality of task performance; \textbf{Provider} is the entity that processes the task with the resources it provided prefer high use rate of resource; \textbf{Platform} it the intermediary entity that promotes the manufacturing activities, it prefers a suitable amount of registered resources to satisfy the needs of the market and an optimal life cycle management of resources. Entities' preferences stimulate the emergence of good resource arrangement pattern that will lead to the emergence operation mode in the cloud manufacturing ecosystem. Hence, it's important to identify a suitable operation mode to meet most of entities' preferences and to optimize the resource management.

In this paper, an original operation mode is designed to describe the basic decision-makings of entity in cloud manufacturing ecosystem, then three extensions, namely metabolism mode, incubation mode and outsourcing mode are proposed. Finally, an experiment to validate these synthetic operation modes are designed using an agent-based simulation method.

### 2016-11-02 review.tex
add response
clearify what to change
add background, need the environmental

% !TEX root = Eco-Model.tex
\section{Review on cloud manufacturing} % (fold)
\label{sec:literature_review}

% This definition is quite abstract and thus despite its corretness not very useful.

In cloud manufacturing context, platform operator can manage  manufacturing service that encapsulated with distributed manufacturing resources intensively with appropriate business model \cite{Xu2012}, modular approaches and multi-layer architectures are the most common approaches to build a cloud manufacturing platform or system framework \cite{Tao2012,Valilai2013}, Lv used the list of views to depict this multi-layer architecture \cite{LvJuly312012-Aug.22012}.

@@

% section literature_review (end)

>>>>

% !TEX root = Eco-Model.tex
\section{Background and literatures} % (fold)
\label{sec:literature_review}
\subsection{Background} % (fold)
\label{sub:background}
1. environmental issues

In cloud manufacturing context, provider entity publishes manufacturing resources, demander entity publishes manufacturing tasks, platform arranges these resources properly to perform the tasks. As one object in research scope of this paper, the mode to generate manufacturing service, which is an arrangement of resources, is discussed along with another object that the mode to keep resource in high quality instead of low quality.

% subsection background (end)

\subsection{Literatures} % (fold)
\label{sub:literatures}

Platform operator can manage manufacturing service that encapsulated distributed manufacturing resources intensively with appropriate business model \cite{Xu2012}, modular approaches and multi-layer architectures are the most common approaches to build a cloud manufacturing platform or system framework \cite{Tao2012,Valilai2013}, Lv used the list of views to depict this multi-layer architecture \cite{LvJuly312012-Aug.22012}.

@@

% subsection literatures (end)
% section literature_review (end)
